Impact of Roe v. Wade’s Overturn: Abortion Restrictions and Infant Mortality in the U.S. Using a Difference-in-Differences Analysis

### 2024-11-29 paper/ExaminingtheimpactOverturnofRoev.Wade:BanningofAbortiononInfantMortalityRatesintheUnitedStatesUsingaDifference-in-DifferencesApproach.qmd
update model card in the paper

Sketches depicting both the desired dataset and the graphs generated in
this analysis is available in the GitHub Repository `other/sketches`.

@@

>>>>

Sketches depicting both the desired dataset and the tables generated in
this analysis is available in the GitHub Repository `other/sketches`.

@@

## Model Card

The model card, referenced from @ozoani2022modelcard, is included in the README under the section titled `Model Card for Infant Mortality and Abortion Policy Analysis Model` for detailed documentation.
